\section{Tài liệu tham khảo}
\begin{thebibliography}{99}

\bibitem{nodc}
Trung tâm Thông tin, dữ liệu biển và hải đảo quốc gia (NODC).  
\url{https://nodc.gov.vn/}

\bibitem{usfws}
U.S. Fish and Wildlife Service (USFWS).  
\textit{Habitat Suitability Index Models}.  
\url{https://www.fws.gov/}

\bibitem{fao_aqua}
Food and Agriculture Organization of the United Nations (FAO).  
\textit{Site selection and carrying capacity for inland and coastal aquaculture}.  
FAO Fisheries and Aquaculture Technical Paper.  
\url{https://www.fao.org/fishery/}

\bibitem{qcvn10}
Bộ Tài nguyên và Môi trường.  
\textit{QCVN 10-MT:2015/BTNMT – Quy chuẩn kỹ thuật quốc gia về chất lượng nước biển}.  
Nhà xuất bản Tài nguyên Môi trường và Bản đồ Việt Nam, 2015.

\bibitem{noaa}
National Oceanic and Atmospheric Administration (NOAA).  
\textit{Habitat suitability and environmental indicators}.  
\url{https://www.noaa.gov/}

\bibitem{epa}
U.S. Environmental Protection Agency (EPA).  
\textit{National Recommended Water Quality Criteria}.  
\url{https://www.epa.gov/wqc}

\bibitem{hsireview}
Roloff, G. J., & Kernohan, B. J. (1999).  
Evaluating reliability of habitat suitability index models.  
\textit{Wildlife Society Bulletin}, 27(4), 973–985.

\bibitem{ecology_hsi}
Store, R., & Jokim{\"a}ki, J. (2003).  
A GIS-based multi-scale approach to habitat suitability modelling.  
\textit{Ecological Modelling}, 169(1), 1–15.

\bibitem{xgboost}
Chen, T., & Guestrin, C. (2016).  
XGBoost: A scalable tree boosting system.  
\textit{Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, 785–794.

\bibitem{ml_timeseries}
Hyndman, R. J., & Athanasopoulos, G. (2018).  
\textit{Forecasting: Principles and Practice}.  
OTexts.  
\url{https://otexts.com/fpp3/}

\bibitem{water_ml}
Li, X., Sha, J., & Wang, Z. (2020).  
Application of machine learning methods in water quality prediction: A review.  
\textit{Water}, 12(6), 1–24.

\bibitem{aquaculture_env}
Boyd, C. E. (2020).  
\textit{Water Quality: An Introduction}.  
Springer, Cham.

\bibitem{heavy_metal}
Förstner, U., & Wittmann, G. T. W. (2012).  
\textit{Metal Pollution in the Aquatic Environment}.  
Springer-Verlag.

\bibitem{gis_aqua}
Kapetsky, J. M., Aguilar-Manjarrez, J., & Jenness, J. (2013).  
A global assessment of potential for offshore mariculture development.  
\textit{FAO Fisheries and Aquaculture Technical Paper}.

\end{thebibliography}


